**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-23 1_Measures.Rmd
update

```{r warning=FALSE}
df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, instruction),
         condition = fct_recode(condition, "Interrogation" = "Social"),
         instruction = fct_relevel(instruction, "TRUTH")) |> 
  group_by(condition, instruction, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()

df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  geom_rect(aes(xmin=1500, xmax=2500, ymin=-65, ymax=90), alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = instruction), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

@@

```{r warning=FALSE}
df <- df |> 
  # Remove participants
  dplyr::filter(Participant != "S9",  # Extreme answers
                !Participant %in% c("S3", "S15", "S19", "S23")) |>  # No data
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore_robust", threshold = qnorm(0.999))),
         Outliers_Physio = as.logical(performance::check_outliers(ECG_Rate_Mean_2.5s, method = "zscore_robust", threshold = qnorm(0.999))))
  ungroup()
```

@@

df$RT[df$Outliers_RT] <- NA
df$ECG_Rate_Mean_2.5s[df$Outliers_Physio] <- NA
```

@@

```{r warning=FALSE, fig.height=figheight*2}
p1 <- df |> 
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p3 <- df |> 
  ggplot(aes(x = ECG_Rate_Mean_2_3s, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2 / p3
```

>>>>

```{r warning=FALSE}
df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
  dplyr::filter(ID != 30) |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, instruction),
         condition = fct_recode(condition, "Interrogation" = "Social"),
         instruction = fct_relevel(instruction, "TRUTH")) |> 
  group_by(condition, instruction, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()

df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = instruction), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

@@

##### Participants

```{r warning=FALSE}
df |> 
  select(Participant, Confidence, RT, HeartRate) |> 
  tidyr::pivot_longer(-Participant) |> 
  ggplot(aes(x=Participant, y=value)) +
  geom_violin(aes(fill=name), color="white", alpha=0.5) +
  geom_jitter(aes(color=name), width = 0.25, height=0, shape="+", size=2) +
  facet_wrap(~name, scales="free", nrow=3) +
  guides(fill="none", color="none")

df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
sum(is.na(df$Confidence)) / nrow(df) * 100
df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
sum(is.na(df$HeartRate)) / nrow(df) * 100
df$RT[df$Participant == "S13"] <- NA # Slower than the others
df$RT[df$RT > 8.25] <- NA # Extreme RT values 
sum(is.na(df$RT)) / nrow(df) * 100
```

##### Observations

```{r warning=FALSE}
df <- df |> 
  # Remove participants
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
  ungroup()
```

@@

df$RT[df$Outliers_RT] <- NA
df$HeartRate[df$Outliers_Physio] <- NA
```

@@

```{r warning=FALSE, fig.height=figheight*2}
p1 <- df |> 
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p3 <- df |> 
  ggplot(aes(x = HeartRate, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2 / p3
```

### 2021-11-23 2_ManipulationChecks.Rmd
update

## Correlation {.tabset}

@@

## Phrasing {.tabset}

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(ECG_Rate_MeanRaw ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

@@

## Lies and RT

- The faster they answer, the more confident they are in their lies.

```{r message=FALSE, warning=FALSE}
# Adjustments for beta models
df$Confidence[df$Confidence == 1] <- 0.99999
df$Confidence[df$Confidence == 0] <- 0.00001

model <- glmmTMB(Confidence ~ RT * Answer + Phrasing + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

## Lies and Heart Rate

- The faster they answer, the more confident they are in their lies.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(ECG_Rate_Mean ~ Confidence * Answer + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("Confidence", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

@@

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
- Effect mostly driven by the social condition that increases the confidence in lies. 
- In other words: harder to lie in the polygraph condition: less obvious feedback cues?

@@

@@

```{r message=FALSE, warning=FALSE}
# ECG_Rate_Mean_2.5s
names(select(df, starts_with("ECG_")))
model <- glmmTMB(ECG_Rate_Mean_1.5_2.5s ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = dplyr::filter(df, abs(ECG_Rate_Mean_1.5_2.5s) < 10))

parameters::parameters(model, effects = "fixed")

modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

>>>>

## Inter-Measures Correlation {.tabset}

@@

### Deception Task and LIE Scale

```{r message=FALSE, warning=FALSE}
r <- df |> 
  select(Participant, Answer, Confidence, RT, HeartRate) |> 
  group_by(Participant, Answer) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
  ungroup() |> 
  select(-Participant) |> 
  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")

### Confidence and RT

- When lying, the faster they answer, the more confident they are.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
```

### Confidence and Heart Rate

- More confidence in truths is associated with higher heart rate.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family()) # warning can be ignored

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### RT and Heart Rate

- No relationship.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

## Effect of Phrasing {.tabset}

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant), data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant), data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant), data = df)

@@

@@

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
- Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?

@@

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

@@

- Higher heart rate in lies vs. truths, and higher heart rate in social condition vs. polygraph.
- No interaction.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

### 2021-11-23 3_ToM.Rmd
update

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", "Confidence"), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
    facet_wrap(~Answer)

@@

@@

@@

@@

@@

p_rt_yoni_total / 
  p_rt_yoni_cognitive / 
  p_rt_yoni_affective / 
  p_rt_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

@@

@@

@@

p_rt_bes_total / 
  p_rt_bes_cognitive / 
  p_rt_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
```

>>>>

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
    facet_wrap(~Answer)

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Total) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "HeartRate")
# p_hr_yoni_total
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Cognitive) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "HeartRate")
# p_hr_yoni_cognitive
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Affective) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "HeartRate")
# p_hr_yoni_affective
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Physical) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "HeartRate")
# p_hr_yoni_physical
```

@@

p_rt_yoni_total / 
  p_rt_yoni_cognitive / 
  p_rt_yoni_affective / 
  p_rt_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_yoni_total / 
  p_hr_yoni_cognitive / 
  p_hr_yoni_affective / 
  p_hr_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Total) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "HeartRate")
# p_hr_bes_total
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Cognitive) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "HeartRate")
# p_hr_bes_cognitive
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Affective) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "HeartRate")
# p_hr_bes_affective
```

@@

p_rt_bes_total / 
  p_rt_bes_cognitive / 
  p_rt_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_bes_total / 
  p_hr_bes_cognitive / 
  p_hr_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
```

### 2021-11-23 4_Intero.Rmd
update

### Accuracy

@@

@@

@@

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_hct_accuracy / 
  p_conf_hct_confidence / 
  p_conf_hct_awareness +
  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_hct_accuracy / 
  p_rt_hct_confidence / 
  p_rt_hct_awareness +
  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

@@

@@

@@

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_maia_total / 
  p_conf_maia_noticing / 
  p_conf_maia_notdistracting / 
  p_conf_maia_bodylistening +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_maia_total / 
  p_rt_maia_noticing / 
  p_rt_maia_notdistracting / 
  p_rt_maia_bodylistening +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
```

>>>>

### Interoceptive Accuracy

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Accuracy) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "HeartRate")
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Confidence) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "HeartRate")
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * HCT_Awareness) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "HeartRate")
```

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_hct_accuracy / 
  p_conf_hct_confidence / 
  p_conf_hct_awareness +
  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_hct_accuracy / 
  p_rt_hct_confidence / 
  p_rt_hct_awareness +
  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_hct_accuracy / 
  p_hr_hct_confidence / 
  p_hr_hct_awareness +
  patchwork::plot_annotation(title = "Heartbeat Counting Task", theme = theme(plot.title = element_text(hjust = 0.5)))
```

## Heartbeat Tracking {.tabset}

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Total) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "HeartRate")
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Noticing) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "HeartRate")
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotDistracting) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "HeartRate")
```

@@

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "HeartRate")
```

### Trusting

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "RT")
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_Trusting) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_trusting <- plot_effect(model, results, var = "MAIA_Trusting", outcome = "HeartRate")
```

### Not Worrying

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "RT")
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_NotWorrying) + (1|Participant), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_notworrying <- plot_effect(model, results, var = "MAIA_NotWorrying", outcome = "HeartRate")
```

### Emotional Awareness

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "RT")
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_EmotionalAwareness) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_emotionalawareness <- plot_effect(model, results, var = "MAIA_EmotionalAwareness", outcome = "HeartRate")
```

### Attention Regulation

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "RT")
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_AttentionRegulation) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_attentionregulation <- plot_effect(model, results, var = "MAIA_AttentionRegulation", outcome = "HeartRate")
```

### Self Regulation

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "RT")
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * MAIA_SelfRegulation) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_hr_maia_selfregulation <- plot_effect(model, results, var = "MAIA_SelfRegulation", outcome = "HeartRate")
```

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*4, fig.width=figwidth*1.5}
p_conf_maia_total / 
  p_conf_maia_noticing / 
  p_conf_maia_notdistracting / 
  p_conf_maia_bodylistening /
  p_conf_maia_trusting / 
  p_conf_maia_notworrying / 
  p_conf_maia_emotionalawareness / 
  p_conf_maia_attentionregulation / 
  p_conf_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_maia_total / 
  p_rt_maia_noticing / 
  p_rt_maia_notdistracting / 
  p_rt_maia_bodylistening /
  p_rt_maia_trusting / 
  p_rt_maia_notworrying / 
  p_rt_maia_emotionalawareness / 
  p_rt_maia_attentionregulation / 
  p_rt_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_maia_total / 
  p_hr_maia_noticing / 
  p_hr_maia_notdistracting / 
  p_hr_maia_bodylistening /
  p_hr_maia_trusting / 
  p_hr_maia_notworrying / 
  p_hr_maia_emotionalawareness / 
  p_hr_maia_attentionregulation / 
  p_hr_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
```

### 2021-11-23 index.Rmd
update

df <- read.csv("data/data_combined.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction)) |> 
  #TODO: This renaming should be done at the preprocessing stage
  rename("Participant" = "ID",
         "Condition" = "condition",
         "Item" = "item",
         "Phrasing" = "style",
         "Answer" = "instruction",
         "YONI_Total" = "yoni_total",
         "YONI_Affective" = "yoni_affective",
         "YONI_Cognitive" = "yoni_cognitive",
         "YONI_Physical" = "yoni_physical",
         "BES_Total" = "BES_total",
         "BES_Cognitive" = "BES_cognitive",
         "BES_Affective" = "BES_affective",
         "HCT_Confidence" = "HCT_confidence",
         "HCT_Accuracy" = "HCT_accuracy",
         "HCT_Awareness" = "HCT_awareness",
         "MAIA_Total" = "MAIA_total",
         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
         "MAIA_BodyListening" = "MAIA_body_listening",
         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
         "MAIA_NotDistracting" = "MAIA_not_distracting",
         "MAIA_NotWorrying" = "MAIA_not_worrying",
         "MAIA_Noticing" = "MAIA_noticing",
         "MAIA_SelfRegulation" = "MAIA_self_regulation",
         "MAIA_Trusting" = "MAIA_trusting",
         "LIE_Ability" = "lie_ability",
         "LIE_Frequency" = "lie_frequency",
         "LIE_Negativity" = "lie_negativity",
         "LIE_Contextuality" = "lie_contextuality",
         "Confidence" = "DT_confidence",
         "RT" = "DT_RT") |> 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)

>>>>

df <- read.csv("data/data_combined_wPhysio.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction)) |> 
  #TODO: This renaming should be done at the preprocessing stage
  rename("Participant" = "ID",
         "Condition" = "condition",
         "Item" = "item",
         "Phrasing" = "style",
         "Answer" = "instruction",
         "YONI_Total" = "yoni_total",
         "YONI_Affective" = "yoni_affective",
         "YONI_Cognitive" = "yoni_cognitive",
         "YONI_Physical" = "yoni_physical",
         "BES_Total" = "BES_total",
         "BES_Cognitive" = "BES_cognitive",
         "BES_Affective" = "BES_affective",
         "HCT_Confidence" = "HCT_confidence",
         "HCT_Accuracy" = "HCT_accuracy",
         "HCT_Awareness" = "HCT_awareness",
         "MAIA_Total" = "MAIA_total",
         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
         "MAIA_BodyListening" = "MAIA_body_listening",
         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
         "MAIA_NotDistracting" = "MAIA_not_distracting",
         "MAIA_NotWorrying" = "MAIA_not_worrying",
         "MAIA_Noticing" = "MAIA_noticing",
         "MAIA_SelfRegulation" = "MAIA_self_regulation",
         "MAIA_Trusting" = "MAIA_trusting",
         "LIE_Ability" = "lie_ability",
         "LIE_Frequency" = "lie_frequency",
         "LIE_Negativity" = "lie_negativity",
         "LIE_Contextuality" = "lie_contextuality",
         "Confidence" = "DT_confidence",
         "RT" = "DT_RT",
         "HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
  select(-HCT_guess, -HCT_noguess, -HCT_onebreath) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

# Adjustments for beta models
df$Confidence[df$Confidence == 1] <- 0.99999
df$Confidence[df$Confidence == 0] <- 0.00001
